Application of computational fluid dynamics and process modelling to investigate low-load operation of a subcritical utility-scale boiler.

### 2022-03-04 ASME_journal/journal-1.1 FINAL/TEXT_SUBMISSION/TEXT_MANUSCRIPT_BRAD_RAWLINS.tex
update - 04/03/2022

%%% use twocolumn and 10pt options with the asme2ej format
\documentclass[twocolumn,10pt]{asme2ej}

\usepackage{graphicx} %% for loading jpg figures
\usepackage{tabu}
\usepackage{float}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{color,soul}
\usepackage{xcolor}

\newcommand{\highlight}[1]{%
  \colorbox{yellow!}{$\displaystyle#1$}}
%% The class has several options
%  onecolumn/twocolumn - format for one or two columns per page
%  10pt/11pt/12pt - use 10, 11, or 12 point font
%  oneside/twoside - format for oneside/twosided printing
%  final/draft - format for final/draft copy
%  cleanfoot - take out copyright info in footer leave page number
%  cleanhead - take out the conference banner on the title page
%  titlepage/notitlepage - put in titlepage or leave out titlepage
%  
%% The default is oneside, onecolumn, 10pt, final

@@

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it To enable the inclusion of intermittent renewable energy sources on existing power grids requires base-load coal-fired power plants to operate flexibly, including fast load changes and continuous low-load operation. Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model. A discretized one dimensional model of the water/steam circuit was developed for the furnace, the radiant superheaters and the convective/back pass heat exchangers. This is coupled with a detailed CFD model incorporating the furnace and radiant superheaters using a Eulerian-Eulerian reference frame. The coupled model is used to investigate the combustion stability, water/steam side effects, and the radiant heat exchanger operational limits for six different burner firing arrangements at a low boiler load of 32\% of Maximum Continuous Rating. The results show that certain firing arrangements can lead to a high risk of fire-side corrosion and overheating of heat exchanger components. Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, a mixed firing arrangement with a higher secondary air mass flowrate for non-firing burners was selected as the best operational strategy at this low load for the boiler under investigation.
}
\end{abstract}

@@

@@

\entry{$f_{heat}$}{Near surface char oxidation fraction [$-$]}
\entry{$f_{p}$}{Forward scattering factor [$-$]}

@@

\entry{$N_{p}$}{Number of particles [$-$]}

@@

\entry{$\alpha_H$}{Mixture void fraction [$-$]}

@@

\entry{$\epsilon_p$}{Particle emissivity [$-$]}

@@

@@

While full scale testing or experimentation on CFPPs is deemed too expensive to pursue, mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions. CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\cite{Gu2020}, \cite{He2007}).

@@

\section{Mathematical model}
\subsection{Computational fluid dynamics modelling}
The present CFD work makes use of a Eulerian-Eulerian approach to capture the distribution of solid and gaseous phase properties such as mass fractions and velocities. The approach is similar to that of the mixture model supplied in ANSYS Fluent v19.5\textsuperscript{\textregistered}, where a single momentum equation is solved for the different phases in the heterogenous mixture. The main difference between the model applied in the current work and the standard mixture model is that the latter solves a single energy equation, whereas the former solves two energy equations, one for the gas phase and another for the solid phase. This is an important feature as it allows the adequate resolution of the temperature-dependent solid fuel combustion processes such as devolatilization and char oxidation, and accurate prediction of particulate radiative heat transfer. Typically, in solid fuel combustion processes the particulate temperature is higher than the surrounding gas temperatures due to the energy release from surface combustion, and incident radiation.
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas-side was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden, it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written below in their respective Reynolds averaged forms.
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\\
&\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{split}
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}

@@

In the present study the realizable k-$\varepsilon$ turbulence model was utilized to address the turbulence closure problem. This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners. The model generally produces higher accuracy results, when compared to the standard k-$\varepsilon$ model, for problems incorporating swirling and separating flows.

The process of coal combustion comprises of four sequential steps namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions. Equations (\ref{eqn_vol_rate}) and (\ref{eqn_vol_arrhenuis}) show the single rate kinetic model utilized in this study, to model the devolatilization process.
\begin{gather}
\frac{dm_{vol}}{dt} = R_{vol}(m_{0,vol}-m_{vol}) \label{eqn_vol_rate} \\
\begin{split}
&R_{vol} = A_{vol}exp\left(\frac{E_{a,vol}}{RT_p}\right)\\
&A_{vol} = 2\times10^5 [s^{-1}]\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
\end{split}
\end{gather}

A devolatilization temperature of 553 [$K$] \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.

@@

The diffusion and kinetic rates of Eqn. (\ref{eqn_char_rate}) are defined in Eqn. (\ref{eqn_char_diff_rate})  and Eqn. (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \cite{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

@@

\begin{table}[h!]
\centering
\caption{Scalar field equation descriptions}\label{tab_scalars}  
\vspace{2mm}     
\begin{tabularx}{3.25in}{p{0.4in} p{1.25in} l}
\hline
Variable &Description& Transport equation \\
\hline
$\phi_{mp0}$ &Original/initial mass of particles& $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{mp0})=0$\\
$\phi_{M}$&Moisture present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{M})=\frac{1}{V} \frac{dm_{evap}}{dt}$\\
$\phi_{VM}$&Volatile matter present in particles&  $\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{VM})=\frac{1}{V}\frac{dm_{vol}}{dt}$\\
$\phi_{FC}$&Fixed carbon present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{FC})=\frac{1}{V}\frac{dm_c}{dt}$\\
$\phi_{ASH}$&Ash present in particles&$\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{ASH})=0$\\
$\phi_{hp}$&Enthalpy of particle&Equation \eqref{eqn_phi_hp}\\
\hline
\end{tabularx}
\end{table}

The energy transport of the pseudo particle phase, is captured by defining a particle phase energy balance equation, which in turn uses the particle enthalpy.
\begin{equation}\label{eqn_phi_hp}
\begin{split}
&\frac{\partial}{\partial x_{i}}( \rho u_{i} \phi_{hp} )=( f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} -\\
&\frac{dm_{evap}}{dt}h_{fg}) \frac{1}{V} 
\end{split}
\end{equation}

The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$. This gives the model the ability to track the particle temperature in the domain, which distinguishes it from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}). The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic. To solve the additional transport equations and their source terms, user defined functions utilized by ANSYS Fluent, were developed using the \textit{C/C++} programming language.

\subsection{Heat transfer modelling}
Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \cite{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in Eqn. (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\begin{split}
&\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \\
&\frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{split}
\end{equation}

@@

It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \cite{Yin2015} respectively.
\begin{figure*} 
\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
\caption{Boiler geometry and layout}
\label{fig_geometry}
\end{figure*}
\begin{figure*}
\centerline{\includegraphics[scale=0.45]{BURNER_MESH}}
\caption{Burner layout and mesh details}
\label{fig_burner_mesh}
\end{figure*}
\begin{figure*}[h!]
\centering
\includegraphics[scale=0.5]{FLOWNEX_SETUP}
\caption{Process model of boiler set-up including the downstream convective components using Flownex SE\textsuperscript{\textregistered} 2021}
\label{fig_flownex}
\end{figure*}
\subsection{Process simulation model}
A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent downstream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021. The data transfer between the two models makes use of a one-way approach, where the CFD simulation data is transferred to the Flownex process model when convergence of each case is achieved, a further explanation of the coupling interface is given in Section  \ref{sec_set_up}. The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls. The model is able to simulate the attemperation flows and momentum transport through the steam/water circuit. The heat exchangers were modelled using a homogeneous two-phase mixture approach, which assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area. The homogeneous mixture fraction and mixture density are defined in Eqn. (\ref{eqn_vol_frac}) and Eqn. (\ref{eqn_mix_rho}) respectively.
\begin{gather}
\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\  
\rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
\end{gather}
Applying the mixture density the following transport equations are solved per process model component;

\begin{equation}\label{eqn_mix_conti}
\frac{\partial}{\partial t}(\rho_M A)+\frac{\partial}{\partial s}(\rho_MAu) = 0
\end{equation}
\begin{equation}\label{eqn_mix_mom}
\frac{1}{A} \frac{\partial}{\partial t}(\rho_M A u)+\frac{1}{A} \frac{\partial}{\partial s}(\rho_M A u^2) = -\frac{\partial p}{\partial s}-\frac{\tau_W P}{A}- \rho_M g \frac{\partial z}{\partial s}
\end{equation}
\begin{equation}\label{eqn_mix_energy}
\begin{split}
&\frac{\partial}{\partial t}(\rho_Mh_M)+\frac{1}{A}\frac{\partial}{\partial s}(\rho_MAuh_M)+\frac{1}{2}\frac{\partial}{\partial s}(\rho_Mu^2)+\\
&\frac{1}{2A}\frac{\partial}{\partial s}(\rho_MAu^3)=\frac{\partial p}{\partial t} + \frac{\dot{Q}_w}{V}-g\rho_Mu\frac{\partial z}{\partial s}
\end{split}
\end{equation}

@@

Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model. This component is used for the heat exchangers downstream of SH3 (refer to Fig. \ref{fig_flownex}). The component model accounts for the radiative (gas and direct), convective and conduction heat transfer mechanisms to and from the gas-side and steam-side control volumes, as well as between up- and downstream heat exchangers on the gas side. The total heat transferred to the water-side control volume can be written as the sum of the absorbed direct radiation and the combined convective and gas radiative heat transfer (i.e. $\dot{Q}_{steam}=\dot{Q}_{abs}+\dot{Q}_{cr}$). The external heat transfer coefficient, from the flue-gas to the heat-exchanger walls makes use of the Gnielinski correlation \cite{Gnielinski2016} for the various heat-exchanger tube arrangements. Figure \ref{fig_heat_exchanger_model} incorporates the direct radiative interactions in each heat-exchanger. It shows that the portion of direct radiation from the preceding heat exchanger that is not absorbed is joined by the bypass radiation ($\dot{Q}_{bypass}$) of the flue-gas control volume which together make up  the direct radiation passed on to the downstream components.
\begin{figure*}[h!]
\centerline{\includegraphics[scale=0.4]{HEAT_EXCHANGER_PROCESS_MODEL}}
\caption{Heat-exchanger component model}
\label{fig_heat_exchanger_model}
\end{figure*}

@@

\begin{table}[h!]
\centering
\caption{Utility boiler fuel characteristics}
\vspace{2mm}
\label{tbl_fuel}
\begin{tabularx}{3.25in}{p{1.5in} p{0.8in} l}
\hline
\textbf{Fuel constituent} & \textbf{Fraction} & \textbf{Unit}\\
\hline
\textit{Ultimate analysis - (DAF)} & \textit{-} & \textit{-}\\
Carbon & $0.7753$ & $kg/kg_{fuel}$\\
Hydrogen & $0.0415$ & $kg/kg_{fuel}$\\
Nitrogen & $0.0181$ & $kg/kg_{fuel}$\\
Oxygen & $0.1474$ & $kg/kg_{fuel}$\\
Sulphur & $0.0175$ & $kg/kg_{fuel}$\\
\textit{Proximate analysis - (AR)} & \textit{-} & \textit{-}\\
Fixed carbon & $0.340$ & $kg/kg_{fuel}$\\
Volatile matter & $0.196$ & $kg/kg_{fuel}$\\
Ash & $0.4090$ & $kg/kg_{fuel}$\\
Moisture & $0.0550$ & $kg/kg_{fuel}$\\
\hline
\textbf{Energy content - (DAF)} & \textbf{Value} &\\
\hline
Higher heating value & $15070$ & $kJ/kg_{fuel}$\\
\hline
\vspace{0pt}
\end{tabularx}
\vspace{-10mm}
\end{table}

@@

\begin{enumerate}
\item Bottom front and rear row burners are fired (Case 1 \& Case 4)
\item Middle front and rear row burners are fired (Case 2 \& Case 5)
\item Bottom front and middle rear row burners are fired (Case 3 \& Case 6)
\end{enumerate}
\begin{table}[h!]
\centering
\caption{Case 1 to 6 model inputs on a per burner basis.}
\label{tbl_case_inputs}
\vspace{2mm}
{\tabulinesep=1.2mm
\begin{tabularx}{3.25in}{p{1.4in} p{0.75in} l}
\hline
Active burners & \textbf{Cases 1 - 3} & \textbf{Cases 4 - 6}\\
\hline
\textbf{Fuel flowrate} [$kg/s$]&3.14  &3.14\\
\textbf{PA flowrate} [$kg/s$]&4.95  &4.95\\
\textbf{SA flowrate} [$kg/s$]&14.85  &14.85\\
\hline
Non firing burners &  & \\
\hline
\textbf{SA flowrate} [$kg/s$]&5.0  &2.5\\
\hline
Input air temperatures& &\\
\hline
\textbf{PA} [$K$]&373  &373\\
\textbf{SA} [$K$]&520  &510\\
\hline
\textbf{Excess air coefficients} & 1.37 & 1.32\\
\hline
\end{tabularx}}

\end{table}

@@

\section{Results \& discussion}
\subsection{Model validation}\label{sec_model_valid}
The validation of the proposed model was conducted for three steady-state MCR loads of 100\%, 80\% and 60\% respectively. Actual plant measurements were used to calculate the thermal heat loads of the three heat exchangers, namely the furnace, platen and final SH, to quantify the accuracy. The model inputs and thermal boundary conditions can be obtained from the studies conducted by Laubscher and Rousseau \cite{Laubscher2019b} \cite{Laubscher2020b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.

@@

\begin{figure*}[h]
\centerline{\includegraphics[scale = 0.4]{VALIDATION}}
\caption{Comparison of experimentally calculated and model heat loads for the furnace, platen SH and final SH}
\label{fig_heat_valid}
\end{figure*}
\begin{figure}[h!]
\centering
\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{COPPM_VALID}}
\hspace{5mm}
\subfigure[]{\includegraphics[width = 3.25in, height =5cm ]{XO2_VALID}}
\caption{Measured and predicted $CO_{ppm}$ (a) and $X_{O_{2}}$ (b) concentrations}
\label{fig_probe_valid}
\end{figure}
Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions. It can be seen that the CFD model can resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location with sufficient accuracy.

>>>>

%%% use twocolumn and 10pt options with the asme2ej format
\documentclass[11pt,cleanfoot]{asme2ej}

\usepackage{tabu}
\usepackage{float}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{color,soul}
\usepackage{xcolor}
\usepackage{enumitem}

\usepackage{graphicx} %% for loading jpg figures
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{helvet}
\usepackage[hyphens]{url}
%\usepackage{hyphens}
\renewcommand{\familydefault}{\sfdefault}
\pagestyle{fancy}
\lhead{{\it Journal of Thermal Science and Engineering Applications}}
\rhead{}
\renewcommand{\headrulewidth}{0pt}
\topmargin 80 pt
\headheight 14 pt
\headsep 30 pt
%\RequirePackage[hyphens]
\usepackage{hyperref}   % to set up hyperlinks
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	citecolor=blue,
	urlcolor=blue,
}
\usepackage[square,numbers]{natbib}
\addtolength{\jot}{3mm}

@@

\maketitle    
\doublespacing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it To enable the inclusion of intermittent renewable energy sources on existing power grids requires base-load coal-fired power plants to operate flexibly, including fast load changes and continuous low-load operation. Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model. A discretized one dimensional model of the water/steam circuit was developed for the furnace, the radiant superheaters and the convective/back pass heat exchangers. This is coupled with a detailed CFD model incorporating the furnace and radiant superheaters using a Eulerian-Eulerian reference frame. The coupled model is used to investigate the combustion stability, water/steam side effects, and the radiant heat exchanger operational limits for six different burner firing arrangements at a low boiler load of 32\% of Maximum Continuous Rating. The results show that certain firing arrangements can lead to a high risk of fire-side corrosion and overheating of heat exchanger components. Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, a mixed firing arrangement with a higher secondary air mass flowrate for non-firing burners was selected as the best operational strategy at this low load for the boiler under investigation.
}
\end{abstract}

@@

\begin{multicols}{2}

@@

\entry{$f_{heat}$}{Near surface char oxidation fraction [-]}
\entry{$f_{p}$}{Forward scattering factor [-]}

@@

\entry{$N_{p}$}{Number of particles [-]}

@@

\entry{$\alpha_H$}{Mixture void fraction [-]}

@@

\entry{$\epsilon_p$}{Particle emissivity [-]}

@@

\end{multicols}

@@

While full scale testing or experimentation on CFPPs is deemed too expensive to pursue, mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions. CFD simulations have been successfully used to model a variety of CFPP boiler types \cite{Laubscher2019a, Gu2020} and cover various aspects such as pollution control \cite{Du2017, Fan2001}, gas-solid flow effects \cite{Chen2017} and boiler retrofitting \cite{Gu2020, He2007}.

@@

\section{Mathematical model}
\subsection{Computational fluid dynamics modelling}
The present CFD work makes use of a Eulerian-Eulerian approach to capture the distribution of solid and gaseous phase properties such as mass fractions and velocities. The approach is similar to that of the mixture model supplied in ANSYS Fluent v19.5\textsuperscript{\textregistered}, where a single momentum equation is solved for the different phases in the heterogenous mixture. The main difference between the model applied in the current work and the standard mixture model is that the latter solves a single energy equation, whereas the former solves two energy equations, one for the gas phase and another for the solid phase. This is an important feature as it allows the adequate resolution of the temperature-dependent solid fuel combustion processes such as devolatilization and char oxidation, and accurate prediction of particulate radiative heat transfer. Typically, in solid fuel combustion processes the particulate temperature is higher than the surrounding gas temperatures due to the energy release from surface combustion, and incident radiation.
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas-side was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden, it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written below in their respective Reynolds averaged forms.
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}

@@

In the present study the realizable k-$\varepsilon$ turbulence model was utilized to address the turbulence closure problem. This model has been successfully used by researchers (\cite{Belosevic2019a, Laubscher2019a, Modlinski2019}), in modelling the effects of coal-fired swirl burners. The model generally produces higher accuracy results, when compared to the standard k-$\varepsilon$ model, for problems incorporating swirling and separating flows.

The process of coal combustion comprises of four sequential steps namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions. Equations (\ref{eqn_vol_rate}) and (\ref{eqn_vol_arrhenuis}) show the single rate kinetic model utilized in this study, to model the devolatilization process.
\begin{gather}
\frac{dm_{vol}}{dt} = R_{vol}(m_{0,vol}-m_{vol}) \label{eqn_vol_rate} \\
\begin{split}
&R_{vol} = A_{vol}exp\left(\frac{E_{a,vol}}{RT_p}\right)\\
&A_{vol} = 2\times10^5 [s^{-1}],\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
\end{split}
\end{gather}

A devolatilization temperature of 553 $K$ \cite{Ranade2015} along with the kinetic parameters (Eqn. \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.

@@

The diffusion and kinetic rates of Eqn. (\ref{eqn_char_rate}) are defined in Eqn. (\ref{eqn_char_diff_rate})  and Eqn. (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \cite{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa],\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

@@

The energy transport of the pseudo particle phase, is captured by defining a particle phase energy balance equation, which in turn uses the particle enthalpy.
\begin{equation}\label{eqn_phi_hp}
\frac{\partial}{\partial x_{i}}( \rho u_{i} \phi_{hp} )=( f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} -\frac{dm_{evap}}{dt}h_{fg}) \frac{1}{V} 
\end{equation}

The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$. This gives the model the ability to track the particle temperature in the domain, which distinguishes it from the thermal equilibrium approach incorporated by previous studies using an EE approach \cite{Benim2005, Vicente2003, Cai2015}. The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic. To solve the additional transport equations and their source terms, user defined functions utilized by ANSYS Fluent, were developed using the \textit{C/C++} programming language.

\subsection{Heat transfer modelling}
Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \cite{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in Eqn. (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{equation}

@@

It is important to note that variable properties for ($\epsilon_p$) and ($f_p$) were used, that are based on the correlations of Lockwood et al \cite{Lockwood1986} and Yin \cite{Yin2015} respectively.

\subsection{Process simulation model}
A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent downstream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021. The data transfer between the two models makes use of a one-way approach, where the CFD simulation data is transferred to the Flownex process model when convergence of each case is achieved, a further explanation of the coupling interface is given in Section  \ref{sec_set_up}. The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls. The model is able to simulate the attemperation flows and momentum transport through the steam/water circuit. The heat exchangers were modelled using a homogeneous two-phase mixture approach, which assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area. The homogeneous mixture fraction and mixture density are defined in Eqn. (\ref{eqn_vol_frac}) and Eqn. (\ref{eqn_mix_rho}) respectively.
\begin{gather}
\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\ 
\vspace{5mm}
\rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
\end{gather}
Applying the mixture density the following transport equations are solved per process model component;

\begin{equation}\label{eqn_mix_conti}
\frac{\partial}{\partial t}(\rho_M A)+\frac{\partial}{\partial s}(\rho_MAu) = 0
\end{equation}
\begin{equation}\label{eqn_mix_mom}
\frac{1}{A} \frac{\partial}{\partial t}(\rho_M A u)+\frac{1}{A} \frac{\partial}{\partial s}(\rho_M A u^2) = -\frac{\partial p}{\partial s}-\frac{\tau_W P}{A}- \rho_M g \frac{\partial z}{\partial s}
\end{equation}
\begin{equation}\label{eqn_mix_energy}
\frac{\partial}{\partial t}(\rho_Mh_M)+\frac{1}{A}\frac{\partial}{\partial s}(\rho_MAuh_M)+\frac{1}{2}\frac{\partial}{\partial s}(\rho_Mu^2)+\frac{1}{2A}\frac{\partial}{\partial s}(\rho_MAu^3)=\frac{\partial p}{\partial t} + \frac{\dot{Q}_w}{V}-g\rho_Mu\frac{\partial z}{\partial s}
\end{equation}

@@

Figure \ref{fig_heat_exchanger_model} illustrates the heat exchanger component process model. This component is used for the heat exchangers downstream of SH3 (refer to Fig. \ref{fig_flownex}). The component model accounts for the radiative (gas and direct), convective and conduction heat transfer mechanisms to and from the gas-side and steam-side control volumes, as well as between up- and downstream heat exchangers on the gas side. The total heat transferred to the water-side control volume can be written as the sum of the absorbed direct radiation and the combined convective and gas radiative heat transfer (i.e. $\dot{Q}_{steam}=\dot{Q}_{abs}+\dot{Q}_{cr}$). The external heat transfer coefficient, from the flue-gas to the heat-exchanger walls makes use of the Gnielinski correlation \cite{Gnielinski2016} for the various heat-exchanger tube arrangements. Figure \ref{fig_heat_exchanger_model} incorporates the direct radiative interactions in each heat-exchanger. It shows that the portion of direct radiation from the preceding heat exchanger that is not absorbed is joined by the bypass radiation ($\dot{Q}_{bypass}$) of the flue-gas control volume which together make up  the direct radiation passed on to the downstream components.

@@

@@

\begin{enumerate}
\item Bottom front and rear row burners are fired (Case 1 \& Case 4)
\item Middle front and rear row burners are fired (Case 2 \& Case 5)
\item Bottom front and middle rear row burners are fired (Case 3 \& Case 6)
\end{enumerate}

@@

\section{Results \& discussion}
\subsection{Model validation}\label{sec_model_valid}
The validation of the proposed model was conducted for three steady-state MCR loads of 100\%, 80\% and 60\% respectively. Actual plant measurements were used to calculate the thermal heat loads of the three heat exchangers, namely the furnace, platen and final SH, to quantify the accuracy. The model inputs and thermal boundary conditions can be obtained from the studies conducted by Laubscher and Rousseau \cite{Laubscher2019b, Laubscher2020b}, where using the same boiler of the present study, they evaluated the thermal performance of the heat exchanging components at full and reduced boiler loads.

@@

Figure \ref{fig_probe_valid} shows the averaged measurement values compared to the CFD predictions. It can be seen that the CFD model can resolve the $CO_{ppm}$ and $X_{O_{2}}$ concentrations at the given probe location with sufficient accuracy.
